---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# prcr

`prcr` is an `R` package for person-centered analysis. Person-centered analyses focus on clusters, or profiles, of observations, and their change over time or differences across factors. See [Bergman and El-Khouri (1999)](http://onlinelibrary.wiley.com/doi/10.1002/(SICI)1521-4036(199910)41:6%3C753::AID-BIMJ753%3E3.0.CO;2-K/abstract) for a description of the analytic approach. See [Corpus and Wormington (2014)](http://www.tandfonline.com/doi/abs/10.1080/00220973.2013.876225) for an example of person-centered analysis in psychology and education.

## Installation

You can install the development version of `prcr` (v. `0.2.0`) from Github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jrosen48/prcr")
```

This version takes a "data-first" approach different from the object-oriented approach used in the version on CRAN. Because of this, **Please note that there presently exists a significant gap in the user interface between the CRAN version available through `install.packages("prcr")` and the in-development version available through GitHub.** This should be addressed shortly in the next CRAN update.

You can install `prcr` from CRAN (v. `0.1.5`) with:

```{r, eval = F}
install.packages("prcr")
```



## Example

This is a basic example using the built-in dataset `pisaUSA15`:

```{r, echo = F, eval = F}
devtools::load_all(".")
```

```{r, eval = T}
library(prcr)
```

```{r example}
df <- pisaUSA15
m3 <- create_profiles_cluster(df, broad_interest, enjoyment, instrumental_mot, self_efficacy, n_profiles = 3)
plot_profiles(m3, to_center = T)
```

Other functions include those for carrying out comparing r-squared values and perfomring cross-validation. These are documented in both the manual and vignette for the CRAN release and their versions in the in-development version will be documented prior to the CRAN release.

## Vignettes

See examples of use of `prcr` in the [vignettes](https://jrosen48.github.io/prcr/articles/index.html).

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct available [here](http://contributor-covenant.org/version/1/0/0/)

## Latent Profile Analyis (LPA)?

This package is being developed along with its sister project, `tidyLPA`, which makes it easy to carry out Latent Profile Analysis by providing an interface to the MCLUST package. More information about `tidyLPA` is available [here](https://github.com/jrosen48/tidyLPA).